rejected_text

### 2024-09-27 paper/rejected-text.qmd
Still working on the draft...

---
title: "Towards caring 15-minute neighbourhoods"
author:
  - name: Anastasia Soukhov 
    email: soukhoa@mcmaster.ca
    affiliations:
        - name: McMaster University
          department: School of Earth, Environment & Society
          city: Hamilton, Canada
    attributes:
        corresponding: true
  - name: Léa Ravensbergen
    email: ravensbl@mcmaster.ca
    affiliations:
        - name: McMaster University
          department: School of Earth, Environment & Society
          city: Hamilton, Canada
  - name: Lucía Mejía Dorantes
    email: lucia.mejia.dorantes@gmail.com
    affiliations:
        - name: Consultant
          city: Karlsruhe, Germany
  - name: Antonio Páez
    email: paezha@mcmaster.ca
    affiliations:
        - name: McMaster University
          department: School of Earth, Environment & Society
          city: Hamilton, Canada
format: 
  docx
  # elsevier-pdf:
  #   keep-tex: true
  #   include-in-header:
  #     text: |
  #       \usepackage{graphicx}
  #       \usepackage{unicode-math}
  #       \usepackage{hyperref}
  #       \def\tightlist{}
  #       \usepackage{setspace}
  #       \doublespacing
  #       \usepackage{lineno}
  #       \linenumbers
  #   journal:
  #     name: 7th International Conference on Women and Gender in Transportation (WGiT)
  #     formatting: preprint
  #     model: 3p
  #     cite-style: authoryear
keywords: ["Accessibility", "Mobility of Care", "Gender", "15-Minute City", "Care Complete Neighbourhoods"]
bibliography: bibliography.bib
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      cache=FALSE)
```

```{r}
#function for creating comments
word_comment <- function(comment, highlight = "") {
  if (isTRUE(knitr:::pandoc_to() == "docx")) {
    paste0('[', comment, ']{.comment-start id="0" author="Anastasia"',
           'date="2024-05-16T15:00:00Z"}', highlight, '[]{.comment-end id="0"}')
  }
}
```

```{r library-setup}
library(biscale)
library(cowplot)
library(sf)
library(here)
library(dplyr)
library(tmap)
library(mapview)
library(tmaptools)
library(pander)
library(flextable)
library(ftExtra)
library(scales)
```

```{r}
load("data/care_dest.rda")
```

```{r reformat care-dest specific categories}
care_dest <- care_dest |> 
  mutate(Care_Category_Specific = case_when(
    Care_Category_Specific  == "Daycare_EarlyON" ~ "Daycare or EarlyON",
    Care_Category_Specific == "Community_Centre" ~ "Community or Recreation Centre",
    Care_Category_Specific == "Daycare_Centre" ~ "Daycare or EarlyON",
    Care_Category_Specific == "Recreation_Centre" ~ "Community or Recreation Centre",
    Care_Category_Specific == "School" ~ "School",
    Care_Category_Specific == "Long-Term_Care_Home" ~ "Long-Term Care or Retirement Home",
    Care_Category_Specific == "Retirement_Home" ~ "Long-Term Care or Retirement Home",
    Care_Category_Specific == "Senior_Centre" ~ "Senior Centre",
    Care_Category_Specific == "Seniors_Active_Living_Centre" ~ "Senior Centre",
    Care_Category_Specific == "Post_Office" ~ "Post Office",
    Care_Category_Specific == "Library" ~ "Library",
    Care_Category_Specific == "Banks" ~ "Bank or ATM",
    Care_Category_Specific == "Grocer_ConvenienceStore" ~ "Convenience Store",
    Care_Category_Specific == "Clinics" ~ "Hospital or Clinic",
    Care_Category_Specific == "Grocer_Retail" ~ "Grocer",
    Care_Category_Specific == "Dentist" ~ "Dentist",
    Care_Category_Specific == "Hosptial" ~ "Hospital or Clinic",
    Care_Category_Specific == "Hospital" ~ "Hospital or Clinic",
    Care_Category_Specific == "Pharmacy" ~ "Pharmacy",
    Care_Category_Specific == "Park" ~ "Park"),
  Care_Category = case_when(
    Care_Category == "Child_Centric" ~ "Dependent-centric",
    Care_Category == "Elder_Centric" ~ "Dependent-centric",
    Care_Category == "Errand_Centric" ~ "Errand-centric",
    Care_Category == "Grocery_Centric" ~ "Grocery-centric",
    Care_Category == "Health_Centric" ~ "Health-centric"))

care_dest <- care_dest |> rename("care_ID" = "ID") |> mutate(care_ID = as.character(care_ID)) 
# care_dest|> st_drop_geometry() |> group_by(Care_Category) |> summarise(count = n())
```

```{r re-weighting points so all destinations are considered spatially equal in access counts, include=FALSE}
Dependent_Centric <- 0.25*2225/1265
Errand_Centric <- 0.25*2225/158
Grocery_Centric <- 0.25*2225/381
Health_Centric <- 0.25*2225/421

#adds up to 2225 opportunities  
0.25*2225/1265*(1265) +  0.25*2225/158*(158) + 0.25*2225/381*(381) + 0.25*2225/421*(421)

#adding the weighted care destination counts -- reweighted such that the 4 categories each make up 25% of the 2225 points.
care_dest <- care_dest |>
          mutate(Dest_count_weighted = case_when(Care_Category == "Dependent-centric" ~ Dependent_Centric,
                                                 Care_Category == "Errand-centric" ~ Errand_Centric,
                                                 Care_Category == "Grocery-centric" ~ Grocery_Centric,
                                                 Care_Category == "Health-centric" ~ Health_Centric))

care_dest$Dest_count_weighted |> sum()
```

# Abstract

The 15-Minute City is a normative conceptualisation gaining ground in urban planning: it frames neighbourhoods as responsive to human needs and environmental sensibilities, where most daily necessities can be reached within a 15-minute walk or bike ride [@Allam2022]. As a related tool, accessibility measures (the ease of reaching opportunities) are increasingly important amongst transport planners aiming to foster just and sustainable cities [@vale2023accessibility]. Both the 15-Minute City and accessibility measures are flexible enough to consider all destination types holistically however, gendered examinations have been lacking in the literature. For instance, accessibility analyses have historically focused on employment-centric and discretionary travel, types of travel more frequent for working-age and higher-income men.

To counter this masculinist bias, this study investigates a way to gender-mainstream the 15-Minute City through a care lens [e.g., @lawWomenTransportNew1999; @cresswell_gendered_2008; @Oestergaard1992; @levy1991towards; @levy2013travel] supported by the Mobility of Care framework (coined by @sanchezdemadariagaMobilityCareIntroducing2013). Mobility of Care emphasizes the importance of travel to unpaid work (care trips) in contrast to the better-studied travel to employment and leisure. While all three trip types (work, care, and leisure) are essential, care trips are often relatively shorter-distance, proximate to residential/work/school, and comprise approximately 30% of adults’ daily trips [@sanchezdemadariagaMeasuringMobilitiesCare2019; @ravensbergen2023exploratory; @mejia2021mobility]; fitting well within the 15-Minute City conceptualisation.

Our study provides an empirical example that maps the 15-Minute City onto the Mobility of Care framework. Specifically, it identifies which areas in Hamilton, Canada are 'caring 15-minute neighbourhoods'. To do so, a database of care destinations is created using secondary data. In this database, care destinations include all places associated with sustaining household tasks needed for the reproduction of life namely: shopping (e.g., groceries), errands (e.g., libraries), health (e.g., dentist), and caring for dependents (e.g., schools). This database is used to estimate the number and mix of care-destinations that can be reached within a 15-minute walk- and cycling- sheds from census centroids. Typologies are generated to illustrate which neighbourhoods can and to what degree facilitate 15-minute access to care.

Results indicate only a few neighbourhoods outside of the downtown core are 'care-complete', i.e., contain a sufficiently high mix of care destinations from all categories and sub-categories. However, some neighbourhoods are almost 'care-complete' and provide 15-minute access to some care categories. Our study frames these neighbourhoods on the continuum of 'caring' and in need of further intervention. The quantitative investigation conducted provides a high-level picture of what neighbourhoods (and their underlying land-use) are connected to transport infrastructure that can support reaching care-destinations.

Taken together, this study provides a theoretical bridge to connect 15-Minute Cities, accessibility analysis and Mobility of Care framework for the purpose of informing policy choice aimed to encourage just and sustainable mobility.

# Introduction

Caring is one of the most fundamental activities in societies, which has allowed humanity to survive and evolve. It involves activities targeted to meet physical, psychological, and emotional needs of others [@ilo_care_2018]. Yet, it is one of the worst devalued, underpaid, and unequal activities worldwide. Traditionally, caring activities have remained on women’s shoulders. Even though the society has evolved, and nowadays women attain higher educational levels and tend to work out of home more than ever before, the bulk of care remains (at any stage of her lifecourse) heavily on her shoulders. The Second Job or the Second Shift remains in all industrial societies, mostly women’s work (Hayden, 1982 (?Citation)) [@hochschild_second_2012].

This unequal share of caring responsibilities leads to gendered differences in among others, career development, differences in contract types and decision-making positions, unbalanced share of women in certain professions, gender pay gap, time poverty, as recognised by different international organisations (European Institute for Gender Equality, 2016 (?Citation)) [@ilo_care_2018]. In fact, already the first feminists in the United States observed that domestic labor was the most relevant basic cause of women’s inequality [@gordon_womans_1976] (Hayden, 1982 (?Citation)).

According to the [@ilo_care_2018], women and girls perform more than three-quarters of the total amount of unpaid care work and two-thirds of care workers are women. The caring economy is part of the women-dominated industries, it is characterised by the evaluative discrimination, which is only one of the dimensions of the gender pay gap [@mejiadorantes_discussing_2019]. Especially in the case of domestic workers, care workers are most of the times women and migrants’ workers, with poor working conditions, and many times associated with informal jobs which imply lack of labour rights, no social and health protection, susceptible of exploitation, one of the poorest working conditions across the care economy as the ILO observes [@ilo_care_2018]. Care workers becomes disrespected, leading to a devaluation of their activity, and consequently remains as one of the less well-paid occupations a person can undertake.

If we turn our attention to the urban planning perspective, Caring is a major human activity that may take form in all urban settings, in all transport modes, all times a day and year, and yet it is not described as neither origin nor destination, and until recently, it was inexistent.

Researchers from various fields have highlighted that western modern industrial societies have imposed a physical separation of the private sphere from the public one, splitting production and reproduction, public and private spaces or simply work and home, concentrating on the economic outcome of being mobile [@cresswell_gendered_2008; @lawWomenTransportNew1999; @levy2013travel; @little_gender_1994; @tronto_toward_1990]. The man with legal rights, paid labour public sphere and woman in the private sphere, dependent, with family duties, personal relations and unpaid labour [@tronto_toward_1990]. In this line, @cresswell_gendered_2008 described how masculinity was related to mobile and active, whereas femininity to static. As an example of this dichotomy, transport planning historically framed non-work/school trips as 'non-mandatory' activities, downgrading these activities in comparison to work.

Women have consistently been found to complete more mobility of care trips than men. In one study, mobility of care comprised 32% of women’s daily trips compared to 28% of men’s. While this gap was significant, it was found to be far greater in lower income households where women complete 20% more care trips than men [@ravensbergen2023exploratory]. This gendered division in mobility of care is perhaps unsurprising as women tend to complete a disproportionate amount of household-serving labour, such as caring for children and other dependents, preparing meals, cleaning, and running errands, when compared to men [@RN4]. This gender gap varies geographically [@RN5]. In Canada, adult women complete 1.9 hours, on average, more of unpaid care than men every day [@RN4]. This labour is essential, and a large component of daily life.

From this research motivation, Sánchez de Madariaga coined the term ‘mobility of care’ in 2013 to refer to all travel required to sustain the needs of a household, such as grocery shopping, escorting children, travelling to health appointments, and running errands [@sanchezdemadariagaMobilityCareIntroducing2013]. While decades of research had examined these unique household-serving trips, her seminal work was the first to consider all these trips as one category. In doing so, she showed how mobility of care is a significant proportion of daily travel. Indeed, in her original work, and in the studies that have followed, it appears that approximately 30% of adults’ trips are for care purposes [@sanchezdemadariagaMobilityCareIntroducing2013; @sanchezdemadariagaMeasuringMobilitiesCare2019; @ravensbergen2023exploratory]. Sánchez de Madariaga not only shows how important these mobility of care trips are, but also highlights the ways in which “mobility of care is systematically under-represented in any analysis of urban transport” (p. 37). Transport surveys and tools do not directly capture mobility of care, which re-enforces the idea that these trips are not a significant part of daily mobility.

Cities have simplified individuals as a universal and neutral entity. As a result, public spaces are differently experienced depending on our multiple identities. Indeed, asymmetric in the distribution of time of citizens is deeply anchored with the public and private spaces organization within cities. In this light, we focus on the potential access to destinations of care through an empirical case study of the mid-sized city of Hamilton, Canada. We acknowledge that caring is composed by actors and activities but aim to spotlight the role that the urban environment plays on our daily lives, on easing our participation and on exercising our rights to the city as individuals with multiple identities. Our work hopes to contribute to a fruitful discussion that may trigger urban and transport policy interventions that increase gender-equity in caring activities among all actors.

<!-- We experience our urban environment depending on our personal characteristics, such as socioeconomic level, education, profession, household responsibilities, physical or mental disabilities, and very importantly, by gender. Furthermore, our living environment is also influenced by historical, economic, social, cultural, political, religion and environmental factors. All these issues have an influence on the way we live and experience the city, on how we participate in the community and on our social relations in the public and private space, on how we invest in our socio-economic development, and finally on our well-being.  -->

<!-- Cities have simplified individuals as a universal and neutral entity. As a result, public spaces are differently experienced depending on our multiple identities. Indeed, the distribution of time of citizens is deeply anchored with the public and private spaces organization within cities. In fact, the asymmetries in the distribution of time of individuals are rooted on city spaces, distances to reach them, transport alternatives and different perceived fears, emotions and constraints, along with the roles typically associated with men and women, together with the gendered division of labour [@villagran_urban_2020]. Furthermore, these authors emphasize that it is a global reality that women invest a greater amount of time to care and to unpaid work and that it is socioeconomically stratified. -->
<!-- Many studies worldwide have documented how gender influences mobility patterns. Men commute longer distances and present direct travel patterns, whereas women present chained trips to accomplish on their way many different activities (for example, dropping children off at schools or daycare, run errands or accompany family members to medical services). For these reasons it has been documented that women tend to have shorter but more complicated transport patterns. They also tend to rely more on public transport whereas men use more private transport [@cresswell_gendered_2008; @levy2013travel; @mejia2021mobility; @the_world_bank_handbook_2020]. Sánchez de Madariaga uses the concept “mobility of care” to recognize, measure, make visible, value and account for all the travel associated to caring and unpaid tasks for the household [@sanchezdemadariagaMobilityCareIntroducing2013]. -->

## Feminist 15-minute neighbourhoods

Within the backdrop of urban planning and 'mobility of care', we connect our work to the 15-minute neighbourhood concept.

The spatial structure of cities and regions has been described in different ways and its advantages and disadvantages has been discussed with regard to a wide variety of issues, for example, regarding health, the environment, economic, social and equity impacts. After the traditional monocentric vision of the city with a core Centre Business District (CBD), other alternatives appeared, especially due to the expansion of cities caused by the automobile and motorized transport. The polycentric urban planning emerged based on the idea of sub-centers (or multiple business centers) with their own services and functions, well-connected among other surrounding areas, where the links between land-use and transport were optimised. Economic activities (such as retail or commercial office development) and job centers played an important role in shaping the spatial structure [@schneider_transit_1981; @sweet_are_2017]. This concept may have different interpretations depending on the spatial and geographical scales [@hall_polycentricity_2009].

In the last decades, the need for more sustainable, healthier, and liveable cities has received more attention. Planners and policy makers have proposed different alternatives where residents reach “essential activities” within walkable or cycling distances, reducing the need for using motorised transportation modes. The 15-minutes cities, 20-minutes or x-minutes cities, have been long under the spotlight. This approach has also received the name of Chrono-urbanism or the “cities of proximity” [@logan_xminute_2022; @moreno_introducing_2021].

In the international context, there are different examples that highlight the importance of good access to different services and amenities within walkable distances. Probably one of the first cities to adopt the proximity approach was Portland. The Portland Plan [@city_of_portland_20minute_2010] was adopted by the City Council on April 25, 2012 aiming at fostering an inclusive city development for the following 30 years. The plan is based on the following principles: prosperity, education, health, and equity. The progress report states that equity should be achieved, an Office of Equity and Human Rights was established focusing on equitable service delivery to all residents. Nonetheless the progress report only measures progress on topics related to racial equity or people with disabilities [@portland_government_portland_2017].

In Paris, the adoption of the 15-Minute city put into the spotlight this approach. In Paris, they targeted six social functions that had to be easily accessible at any part of the city: housing, work, health care, groceries, education and leisure [@ville_de_paris_paris_2022]. In 2021, Ottawa also adopted a 15-Minutes approach in the new City of Ottawa Official Plan [@ville_dottawa_quartier_2021].

More recently, @moreno_introducing_2021 considers four dimensions on how the 15-minute city framework: density (in terms of people per sq.km); diversity (including mixed-land use and diversity of people; the temporal and spatial proximity to essential services (residential areas, work, commercial areas, education centres, health facilities and other basic institutions) and digitalisation.

It can be observed that the feminist perspective of the cities of proximity is still underestimated. Only few examples exist that specifically target this issue [@gil_sola_choose_2022; @macintyre_her_2022].

Even if we are on the right direction to facilitate caring activities, develop human-centred urban areas, the chrono-urbanism needs to set the ground on aspects that specifically target caring activities and gender. Similarly, it is necessary to provide alternatives to measure progress on this important issue. On the other hand, an intersectional approach to understand how different personal identities interact in our daily day activities in the cities is necessary. There is still room for improvement.

## Mobility of care and mode-constraints

Given that almost one third of daily trips are for care purposes [@sanchezdemadariagaMobilityCareIntroducing2013], it is important to plan for mobility of care. There are also equity considerations to consider: as discussed, women, and especially low-income women, complete this travel more than men. Planning for mobility of care may also warrant different considerations because mobility of care trip characteristics differ from other trips, notably those of the commute to work. For instance, many of these trips are made through trip-chains, i.e., when a non-work-related stop is made during the commute. Women have been found to do so more than men, which is understood as being due to their need to balance unpaid-household serving care and paid employment (e.g., picking up groceries or children on the way home from work) [@ravensbergen2023exploratory; @scheinerWomenComplexDaily2015].

Further, compared to the trip to work, mobility of care trips are more frequently completed by car and by foot, and less frequently done by transit or bicycle [@ravensbergen2023exploratory]. Evidence for why this modal difference is observed exists. For instance, it is possible that walking is more common for care than for work trips because care trips tend to be short [@ravensbergen2023exploratory]. In other words, if care destinations are closer to the home, it is more likely that these destinations are walkable. Ample literature examines the benefits and barriers to walking care destinations, such as schools (e.g., [@RN7;@RN8;@RN9]) and grocery stores (e.g., [@RN10;@RN11]). Little of this work uses the mobility of care framework. Instead, it tends to consider singular care destinations in research focusing on walkability.

@@

It appears that the car is the preferred travel mode for mobility of care. In one study, car use was higher for mobility of care trips than the commute to work (82.3% vs. 74.7%) [@ravensbergen2023exploratory]. Further, the rate of car use is higher amongst trips that are part of a chain than those that are not (85.28% v. 78.09%) [@ravensbergen2023exploratory]. Some studies found that a car is viewed as the easier way to incorporate unpaid mobility of care into one’s daily travel as it provides convenience and mitigates concerns about traffic and stranger danger [@maciejewskaHaveChildrenThus2019, @carverParentalChauffeursWhat2013]. Others, however, have found that women are more likely to complete household-serving travel duties by alternative modes than men due to their lower car access [@RN24;@RN25]. It seems that car use may be preferred for mobility of care trips, but planning mobility of care for the car may leave those who do not have access to a car, many of them low-income women, with difficult mobility of care trips.

@@

Taken together, there appears to be a preference for travel by car for mobility of care trips. This is problematic, however, in at least two major ways. First, cars are less sustainable than other modes of transport. Normalizing car use for care trips does not advance the low-carbon transport transition that most cities are aiming for (at least in principle!). Since care trips tend to be short, they are also perfect candidate to be completed by bus, bicycle, or by foot. That is, if these alternative and sustainable modes are planned with care in mind. Second, there is equity concerns with assuming people are accessing care destinations by car. Many people, and low-income women in particular, do not have access to a car. Some are also experiencing a degree of spatial entrapment. Having safe and convenient access to care destinations using alternatives to the private car is especially important for those who must rely on these options regardless of whether they are well planned.

# Data and Methods

## Case study context
In Canada, women have become more educated and have an achieved an increased participation in the labour market [@government_of_canada_gender_2023]. In fact, the educational level of women has surpassed most men [@government_of_canada_women_2023]. Reports observe that the gender pay gap has narrowed but disparities persist [@drolet_intersectional_2023;@pay_equity_office_gender_2023]. According to the statistics, in Ontario between 1998 to 2022 the gender gap narrowed but still women make 87 cents on average for every dollar made by a man [@pay_equity_office_gender_2023]. All reports observe that it affects women differently, women with disabilities, immigrants, indigenous or racialized suffer especially from the gender pay gap. Similarly to other countries worldwide, the occupational segregation remains and women are segregated into lower paid job classes and there is a dominance of women in minimum wage jobs [@drolet_intersectional_2023]. Furthermore, women are underemployed, and make up most part-time work. In this respect, the lack of childcare alternatives enforces this obligatory part-time work [@equal_pay_coalition_myths_2022]. All researchers and organisations agree that an intersectional approach is of utmost importance to better plan policies to enforce gender equality.

- Next: describe hamilton's land-use context; communities which are urban, rural, suburban. Also describe the residential parcels summary statistics, ~140,000 points, aggregated at the level of Canadian Census DA. See population descriptive plots in @fig-Fig1:
```{r plot-figure1, out.width=600, out.height=600}
#| label: fig-Fig1
#| fig-cap: "The number of residential parcels per DA in 2020 (top) and the rate of population per dwelling per DA (middle) and prevalence of Low-income cut-offs after-tax (LICO-AT) per DA (bottom) retrieved from the 2021 Canadian Census. All scales in quartiles. Basemap shapefiles are sourced from the Open Data Hamilton Portal [@opendatahamiltonCityBoundary2023] and the USGS [@greatlakesUSGS2010]."
knitr::include_graphics("data/pop_descriptive_plots.tiff")
```

## Estimated travel times
- Next: describe the estimated 15-minute walk travel times using {r5r}, from all residential parcel points to all care destinations assuming default walking speed and OSM road network for Hamilton. Provide summary statistics.

>>>>

---
title: "rejected_text"
format: html
---

The "15-Minute City" has been recently adopted by leaders as a way to promote human-scaled cities. As defined in @moreno_introducing_2021, the 15-Minute City is a urban planning model based in chrono-urbanism, a theory that emphasizes the positive impact on quality of urban life when urban space becomes multi-rythmic [related to chronotopy @mulicekUrbanRhythmsChronotopic2015]. Multi-rhythmic urban space is in opposition to industrial Fordism and single-use zoning [@mulicekUrbanRhythmsChronotopic2015; @morenoVilleQuartHeure2016]; the segregation of urban time and space for individual uses and mobility. The 15-Minute City thus one that accommodates the ability to reach essential destinations such as shops, work, and healthcare within a walkable radius. It would allow individuals to reclaim time spent on car mobility and give way to sustainable modes; prompting urban spaces that are responsive to human needs and environmental sensibilities [@Allam2022]. The 15-Minute City generated much interest in planning practice and public discourse, especially after Paris mayor Anne Hidalgo proposed a 15-minute city plan in her 2020 re-election campaign. Though the term 15-Minute City is relatively new, neighbourhood planning is not (e.g., Perry's Neighbourhood Unit Concept (NUC) from the 1930s [@kissfazekasCircleParadigms15minute2022], 15-minute neighbourhoods in China (X)). A critique of neighbourhood planning approaches have been their top-down nature [@talenSocialSciencePlanned2017]. The 15-Minute City esposes to be different, however top-down planning questions of how to equitable select travel-time thresholds (15 minute, or something else?), by what sustainable mode, to what destinations, and for whom continue to plague proximity-based urban planners.

While much care labour takes place in the private and feminised sphere, completing care activities requires one to be mobile. In other words: caring for oneself and others requires trips to, amongst other places, grocery stores, day cares, elder care, and health care destinations.

@moreno_introducing_2021 considers four dimensions on how the 15-minute neighbourhood framework: density (in terms of people per km$^2$); diversity (including mixed-land use and diversity of people); the temporal and spatial proximity to essential services (residential areas, work, commercial areas, education centres, health facilities and other basic institutions) and digitalisation.

<!-- These critiques were supported by case studies of planned neighbourhoods as... lead to social segregation of classes, destination functions, and automobile use. From it's onset, it was an efficient way to develop housing after the Second World War. The emphasis of proximity to some 'daily essentials' but disconnection from specialised activites (e.g., work) paved the way for car-based subrbia.  by capital of cities. Can the neighbourhood form might be seen as a vehicle for capitalist exploitation, gentrification and displacement??? The place of neighbourhood planning is actively being debated: can it's social crtiques be addressed in the new form as a "15-Minute City"? This study seeks to contribute to this decades old debate. -->

Before discussing 'what outcome', we first ask 'what amenity' as the focus of this study. Often, accessibility analysis studies have focused on a single amenity type (X), often employment destinations and often focused on a scale beyond the neighbourhood. However, due to 15-Minute City's emphasis on proximate-level service provision, recent academic work on the topic has employed accessibility analysis to account for multiple 'local' amenities types, but seldom included employment. We argue that the inclusion of employment opportunities into the 15-Minute City conceptualisation is critical to it's definition. Why? We echo critics made by planners and social scientistics in decades past: neighbourhoods that did not mix work with service and culture within the neighbourhood, paved the way for car-based suburbia: cars allowed for the connection of neighbourhoods with their 'lower-order' amenities to areas with 'high-order' destinations like work (X). The lower- and higher- order framing of these destinations supported the continued segregation of urban life across many dimensions (X).

Combing all amenity types into the 15-Minute City concept is also a matter of gender equality. There is a branch of research that encompases this critique: Mobility of Care. This framework encourages the explicit consideration of destination types that serve unpaid labour (care destinations) into transport planning (as opposed to only considering destinations with paid work). Not considering these care destinations have travel time (and hence quality of life) implications on those who do care activites, commonly women and especially disadvantaged women. The consideration of _what_ amenity type is a gender issue.

From this position, this study aims to holistically investigate the ease of interacting with proximate amenities (accessibility) from the perspective of the 15-Minute City and the Mobility of Care framework. As mentioned, accessibility analysis have typically focused on employment (X) and recent 15-Minute City flavoured analysis focus on 'lower-order' amentities. We focus on a case study of the mid-sized City of Hamilton, Canada, and aim to classify areas by what degree they may be considered a '15-Minute Neighbourhood" based on the relative quantity of amenity access and diversity of access. We offer a novel methodology of holistically considering all proximate-amenities, offer empirical findings, and contribute theoretically to the ongoing debate on the definition of a 15-Minute City by foregrounding care destinations.

The objectives of the paper are as follows:

1)	To examine the potential accessibility to, and diversity of, care destinations in the case study. We identify to what degree are neighbourhoods caring and/or complete. To do so, we make use of self organizing maps (SOM), an unsupervised machine learning data-dimensionality reduction technique to identify caring and complete neighbourhoods.
2)	We then apply the same SOM methodology to determine profiles of population groups to understand who enjoys these neighbourhoods and who does not.

In this way, destinations outside of the home involved in caring activities has important implications for spatial and transportation planning; for all people but especially for all women and those from lower income households who complete the most mobility of care trips [@ravensbergen2023exploratory].

 In fact, early feminists in the United States had already observed that domestic labor was the single most relevant cause of women’s inequality in society [@gordon_womans_1976; @haydenGrandDomesticRevolution1982]. .... Sánchez de Madariaga not only shows how important these mobility of care trips are, but also highlights the ways in which “mobility of care is systematically under-represented in any analysis of urban transport” (p. 37). Transport surveys and tools do not directly capture mobility of care, which re-enforces the idea that these trips are not a significant part of daily mobility. .... In this way, destinations outside of the home involved in caring activities has important implications for spatial and transportation planning; for all people but especially for all women and those from lower income households who complete the most mobility of care trips [@ravensbergen2023exploratory].

Care also has important implications for spatial and transportation planning. Indeed, researchers from various fields have highlighted that western modern industrial societies have imposed a physical separation of the private sphere from the public one, splitting production and reproduction, public and private spaces or simply work and home, concentrating on the economic outcome of being mobile [@cresswell_gendered_2008; @lawWomenTransportNew1999; @levy2013travel; @little_gender_1994; @tronto_toward_1990]. Men tend to be associated with legal rights, paid labour, and the public sphere while woman are associated with the private sphere, dependents, family duties, personal relations and unpaid labour [@tronto_toward_1990]. In this line, @cresswell_gendered_2008 described how masculinity has been constructed as mobile and active, whereas femininity is static. As an example of this dichotomy, transport planning has historically framed non-work/school trips as 'non-mandatory' activities, downgrading these activities in comparison to mandatory trips like work and school (XXX). In more recent years, planners have begun to resist the spatial separation of the public and private sphere to promote for sustainable cities. Proximity planning has become more normalized, a popular example is the 15-minute neighbourhood i.e., neighbourhoods where residents can reach all necessary destinations within a 15-minute active transport trip. The 15-minute neighbourhood concept, however, has yet to foreground care.

<!-- The spatial structure of cities and regions has been described in different ways and its advantages and disadvantages has been discussed with regard to a wide variety of issues, for example, regarding health, the environment, economic, social and equity impacts. After the traditional monocentric vision of the city with a core Centre Business District (CBD), other alternatives appeared, especially due to the expansion of cities caused by the automobile and motorized transport. The polycentric urban planning emerged based on the idea of sub-centers (or multiple business centers) with their own services and functions, well-connected among other surrounding areas, where the links between land-use and transport were optimised. Economic activities (such as retail or commercial office development) and job centers played an important role in shaping the spatial structure [@schneider_transit_1981; @sweet_are_2017]. This concept may have different interpretations depending on the spatial and geographical scales [@hall_polycentricity_2009]. -->

Within the backdrop of urban planning and ‘mobility of care’, we connect our work to the 15-minute neighbourhood concept.

Both the 15-minute neighborhood and accessibility measures are flexible enough to consider all destination types holistically, however, gendered examinations have been lacking in the literature. For instance, accessibility analyses have historically been employment-centric even when adopting a gendered perspective [@paez_jobs_2013]. Some 15-minute city analyses focus on care destinations, but they seem to not put care at the forefront, or to consider but one care destination (e.g., [@hosford15minuteCityReach2022] on grocery stores). Though few 15-minute neighbourhood analyses are explicitly feminist, their potential to build feminist communities have been noted outside of academia. For instance, Women in Urbanism have noted how women may benefit more than men from this 15-minute approach to planning. For instance, women tend to walk and use transit more than men, as well as to make more frequent, but shorter trips -and often as part of a chain (i.e., with stops along the way). These trip characteristics are all well served in 15-minute frameworks. 15-minute neighbourhoods also promote walkability, which results in more “eyes on the streets” and its associated safety, an important enabler of mobility for women and girls. Finally, because women tend to earn less money than men and cars are a large financial burden, planning paradigms that reduce car dependency, such as 15 minute cities, may on average benefit women more than men [@Bertolo2023].

-- 
# possible discussion

@@

It appears that the car is the preferred travel mode for mobility of care. In one study, car use was higher for mobility of care trips than the commute to work (82.3% vs. 74.7%) [@ravensbergen2023exploratory]. Further, the rate of car use is higher amongst trips that are part of a chain than those that are not (85.28% vs. 78.09%) [@ravensbergen2023exploratory]. Some studies found that a car is viewed as the easier way to incorporate unpaid mobility of care into one’s daily travel as it provides convenience and mitigates concerns about traffic and stranger danger [@maciejewskaHaveChildrenThus2019, @carverParentalChauffeursWhat2013]. Others, however, have found that women are more likely to complete household-serving travel duties by alternative modes than men due to their lower car access [@RN24;@RN25]. It seems that car use may be preferred for mobility of care trips, but planning mobility of care for the car may leave those who do not have access to a car, many of them low-income women, with difficult mobility of care trips. Studies also observe disparities regarding gender mobility and type of activities, depending on the area of residence; women living in the city center, where more transport systems and activities are available, use more sustainable travel modes than the ones living in the outskirts, which tend to rely more on cars to carry out daily activities [@marquet2014walking; @mejia2021mobility; @montero2023role; @montero2023applying]. Outer areas are not as dense as in the downtown, and are basically car-oriented developments. Thus, studies observe that in the outer areas gender equity is confronted to sustainable mobility.

@@

Taken together, there appears to be a preference for travel by car for mobility of care trips in many geographical contexts. This is problematic, however, in at least two major ways. First, cars are less sustainable than other modes of transport. Normalizing car use for care trips does not advance the low-carbon transport transition that most cities are aiming for (at least in principle!). Since care trips tend to be short, they are also perfect candidate to be completed by bus, bicycle, or by foot. That is, if these alternative and sustainable modes are planned with care in mind. Second, there is equity concerns with assuming people are accessing care destinations by car. Many people, and low-income women in particular, do not have access to a car. Some are also experiencing a degree of spatial entrapment. Having safe and convenient access to care destinations using alternatives to the private car is especially important for those who must rely on these options regardless of whether they are well planned.

## about employment.

Though not considered, employment is a promiment destination type not considered within this work. However, as mentioned, care activites are often trip-chained. therefore, the availability of care destinations around work also matter. This is for future investigation.

In Canada, women have become more educated and achieved increased participation in the labour market [@government_of_canada_gender_2023]. In fact, the educational level of women has surpassed most men [@government_of_canada_women_2023]. Reports observe that the gender pay gap has narrowed but disparities persist [@drolet_intersectional_2023;@pay_equity_office_gender_2023]. For instance, in the province of Ontario women still make 87 cents on average for every dollar made by a man and by all reports women of inter-sectional marginalized identies are more impacted [@pay_equity_office_gender_2023]. Similarly to other countries worldwide, the occupational segregation remains and women are segregated into lower paid job classes and there is a dominance of women in minimum wage jobs [@drolet_intersectional_2023]. Furthermore, women are underemployed, and make up most part-time work. In this respect, the lack of childcare alternatives enforces this obligatory part-time work [@equal_pay_coalition_myths_2022]. All researchers and organisations agree that an intersectional approach is of utmost importance to better plan policies to enforce gender equality.

# possibel conclusions

Cities have simplified individuals as a universal and neutral entity. As a result, public spaces are differently experienced depending on our multiple identities. Indeed, asymmetric in the distribution of time of citizens is deeply anchored with the public and private spaces organization within cities. In this light, we bring together the literatures on 15-minute cities and mobility of care by focusing on the potential access to destinations of care through an empirical case study of the mid-sized city of Hamilton, Canada. We acknowledge that caring is composed by actors and activities but aim to spotlight the role that the urban environment plays on our daily lives, on easing our participation and on exercising our rights to the city as individuals with multiple identities. Our work hopes to contribute to a fruitful discussion that may trigger urban and transport policy interventions that increase gender-equity in caring activities among all actors.

```{r plot-figure6-create, eval=FALSE}
plot1 <- ggdraw() + draw_image(glue::glue(here::here(), "/figures/access_sc_plot_2.png"))
plot2 <- ggdraw() + draw_image(glue::glue(here::here(), "/figures/access_sc_plot_1.png"))
plot3 <- plot_grid(plot1, plot2)

ggsave(glue::glue(here::here(), "/figures/access_sc_plot_combo.png"), dpi=300)
```

```{r plot-figure6, out.width=800, out.height=800}
#| label: fig-Fig6
#| fig-cap: "The 5 resulting superclusters from the SOM output (left) and the associated dendrogram structure (right)."
#| 
knitr::include_graphics(glue::glue(here::here(), "/figures/access_sc_plot_combo.png")) 
```
